Deconstructing Simple and Choice Decision and Movement Time Across the Spectrum of Schizophrenia Genetic Risk

### 2022-12-21 analysis/paper/elsevier/paper-elsevier.qmd
i hate docker and everything

format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
  pdf:
    cite-method: biblatex
  arxiv-pdf:
    keep-tex: true  
    linenumbers: false
    doublespacing: false
    runninghead: "Schizophrenia Reaction Time"
    cite-method: biblatex
  arxiv-html: default
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Biological Psychiatry
      formatting: preprint
      model: 3p
      layout: onecolumn
      cite-style: number
      graphical-abstract: "![](abstract.png)"
      highlights:
        - Highlight 1
        - Highlight 2 
        - Highlight 3
    include-in-header: 
      text: |
        \newpageafter{author}

>>>>

format: 
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Biological Psychiatry
      formatting: preprint
      model: 3p
      layout: onecolumn
      cite-style: number
      graphical-abstract: "![](abstract.png)"
      highlights:
        - Highlight 1
        - Highlight 2 
        - Highlight 3
    include-in-header: 
      text: |
        \newpageafter{author}

### 2022-12-21 analysis/paper/paper.qmd
i hate docker and everything

---
title: "Deconstructing Simple and Choice Decision and Movement Time Across the Spectrum of Schizophrenia Genetic Risk"
author:
  - Joey Trampush:
      correspondence: "yes"
      email: joey.trampush@med.usc.edu
      orcid: 0000-0003-0830-508X
      institute:
        - usc
        - nimh
  - Samantha Fleck:
      institute: usc
      orcid: 0000-0000-0000-0000
  - Dwight Dickinson:
      institute: nimh
      orcid: 0000-0003-1689-0559
  - Juan Pérez:
      orcid: 0000-0003-1689-0551
      institute:
        - name: usc
  - Max Mustermann:
      orcid: 0000-0003-1689-0552
institute:
  - usc:
      name: Keck School of Medicine of USC
      address: 23 Science Street, Eureka, Mississippi, USA
  - nimh: National Institute of Mental Health
title-block-published: "Last updated"  
date: now
date-format: long

format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
  pdf:
    cite-method: biblatex
  arxiv-pdf:
    keep-tex: true  
    linenumbers: false
    doublespacing: false
    runninghead: "Schizophrenia Reaction Time"
    cite-method: biblatex
  arxiv-html: default
  elsevier-pdf:
    keep-tex: true

execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  schizophrenia; reaction time; keyword 3
highlights: |
  These are the highlights. 
---

@@

```{r clean}
source("R/clean.R")
# see R/clean.R
# this chunk (as long as it is empty, comments don't count) runs external
# code from scripts listed in the YAML
# see also https://yihui.org/knitr/demo/externalization/
```

```{r srt-hc}
summary(srt_hc$moart_simple_right_rt)
```

@@

```{r}
#| label: srt-r
#| echo: false
library(ggplot2)
ggplot(srt_hc, aes(moart_simple_right_rt, moart_simple_right_mt)) +
  geom_point() +
  theme_minimal() +
  NULL
```

>>>>

---
title: "Deconstructing Simple and Choice Decision and Movement Time Across the Spectrum of Schizophrenia Genetic Risk"
author:
  - name: Joey W. Trampush
      email: joey.trampush@med.usc.edu
      institute: 
        - id: usc
          name: Some Institute of Technology
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
      attributes:
        corresponding: true
      note: This is the first author footnote.
      orcid: 0000-0003-0830-508X

  # - Joey Trampush:
  #     correspondence: "yes"
  #     email: joey.trampush@med.usc.edu
  #     orcid: 0000-0003-0830-508X
  #     institute:
  #       - usc
  #       - nimh
  - Samantha Fleck:
      institute: usc
      orcid: 0000-0000-0000-0000
  - Dwight Dickinson:
      institute: nimh
      orcid: 0000-0003-1689-0559
  - Juan Pérez:
      orcid: 0000-0003-1689-0551
      institute:
        - name: usc
  - Max Mustermann:
      orcid: 0000-0003-1689-0552
institute:
  - usc:
      name: Keck School of Medicine of USC
      address: 23 Science Street, Eureka, Mississippi, USA
  - nimh: National Institute of Mental Health
title-block-published: "Last updated"  
date: now
date-format: long

format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
  pdf:
    cite-method: biblatex
  # arxiv-pdf:
  #   keep-tex: true  
  #   linenumbers: false
  #   doublespacing: false
  #   runninghead: "Schizophrenia Reaction Time"
  #   cite-method: biblatex
  # arxiv-html: default
  # elsevier-pdf:
  #   keep-tex: true

execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 600
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  schizophrenia; reaction time; keyword 3
highlights: |
  These are the highlights.
pdf-engine: pdflatex
---

@@

```{r clean}
#source("R/clean.R")
# see R/clean.R
# this chunk (as long as it is empty, comments don't count) runs external
# code from scripts listed in the YAML
# see also https://yihui.org/knitr/demo/externalization/
```

```{r srt-hc}
#summary(srt_hc$moart_simple_right_rt)
```

@@

```{r}
#| label: srt-r
#| echo: false
# library(ggplot2)
# ggplot(srt_hc, aes(moart_simple_right_rt, moart_simple_right_mt)) +
#   geom_point() +
#   theme_minimal() +
#   NULL
```
